Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-18 paper/ijcai/paper.tex
paper with statistical tests

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.

@@

% Single author syntax
%\author{Jérôme Lang\\ 
%Laboratoire d'Analyse et Modélisation des Systèmes pour l'Aide à la Décision (LAMSADE)  \\
%pcchair@ijcai-18.org}

% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)

@@

\begin{abstract}
  \Sof{@todo}
\end{abstract}

@@

%\Sof{Elaborate more on the advantages of the SFL+DS combination and how DS helps SFL being more efficient}

%% PROBLEM MOTIVATION
Software debugging is difficult. The task of locating the faulty code
(\ie{}, fault localization) is particularly challenging. For that
reason, countless automated techniques have been proposed in the past
to reduce the cost of fault localization.

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic Slicing ~\citeauthor{Agrawal:1990:DPS:93542.93576} looks for the statements
in code that influence the evaluation of the fault-revealing
assertion. Although the technique has been intensively investigated in
research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
exception.  \sfl{}~\cite{7390282}, in contrast, does not try to
recover the influence region of faulty statements. It is a black-box
statistical fault localization method that computes suspiciousness
values associated with program entities (e.g., basic blocks). For
that, it uses coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in decreasing
order of suspiciousness. Similarly to \ds{}, \sfl{} received
tremendous attention over the years, but its applicability to support
debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been
shown useful in supporting downstream analyses, such as Automated
Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for fixes to buggy
statements. Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes.

%Recent \apr{} techniques use \sfl{} to guide
%the search for repairs .

%% \Fix{Revise this $\rightarrow$} Mao and Wang
%% \cite{lei-mao-dai-wang-2012} had promising results compared to \sfl{}
%% state of the art techniques, such as Tarantula [cite] and Ochiai
%% [cite], concerning the relative percentage of the code above the
%% fault. Prior work used the same measurement approach
%% \cite{santelices-jones-yu-harrold-2009,wang-cheung-chan-zhang-2009,jones-2005}.
%% However, the problem with this approach lies in the effort to find the
%% defect, as shown on Parnin and Orso's study \cite{parnin-orso-2011},
%% in which a percentage rank does not scale with the size of a
%% codebase. For example, if a fault statement is ranked on the 83rd
%% position as a result of a \sfl{} technique, the percentage rank using
%% a codebase of 8300 LOC is only 1\%, with the amount of absolute lines
%% of code to be examined not being considered.  This can result in
%% millions of lines of code to be analysed, proving that a percentage
%% rank is not a practical evaluation metric
%% \cite{ang-perez-van-deursen-rui-2017}.  \Fix{end here}

%% For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
%% reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
%% rankings when using dynamic slicing in combination with \sfl{} versus
%% plain \sfl{}.

@@

The contributions of this work are as follows:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
%	\item Insights into the use of top-k metric to evaluate the classes with the highest suspiciousness ranks.
	\item The tools used to run the study. Benchmarks and experimental results are also publicly available.
\end{itemize}

@@

%% To select a slicer implementation to run our experiments, we
%% considered two criteria: robustness as to support non-trivial programs
%% and efficiency as to support execution of our experiments in
%% reasonable time.  Unfortunately, we failed to find public
%% implementations satisfying these criteria.
%% For those reasons, we ded to implement a critical slicer for Java,
%% which is the language of the subjects in our dataset, \dfj{}.

@@

We used the Mozilla Lithium tool~\footnote{ Lithium is available at \url{https://github.com/MozillaSecurity/lithium} (accessed November 2018).} as the implementation
for Critical Slicing. Lithium is conceptually similar to the DD-min
Delta Debugging algorithm~\cite{zeller-hildebrandt-tse2002}, but
operates on code instead of test inputs. It takes as input a file and
produces as output a simplified version of that file that satisfies a
user-defined oracle. For dynamic slicing, the oracle is defined such
that the test produces the same failure manifestation. The Lithium
minimization process starts by determining the initial size of
chunks---in number of lines---to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search
looking for chunks to remove from the file that satisfy the
oracle. When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more line can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs can be found elsewhere\footnote{ Algorithm complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (accessed November 2018).}.

%% Despite that, optimizations are important to
%% make a Critical Slicing implementation efficient. We describe the
%% optimizations we used in the following.

%% The output we used to determine equivalence of the original failing
%% execution and the sliced failing execution was the stack trace
%% produced by the assertion violation.  It is important to note that
%% Binkley \etal{} recently proposed the critical slicer
%% ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}, but its design sacrifies
%% efficiency (important to run our experiments) for generality. Some of
%% the slicing jobs we ran on ORBS took hours to run. For example,
%% \Fix{...elaborate...}

%% \vspace{1ex}\noindent\textbf{Blackbox slicing.} Removing statements
%% from the program is necessary to discover whether it is essential
%% to the execution or not. For that reason, we compare the test stack
%% trace to look for changes in the output. Considering one execution,
%% if one line of the stack trace changes and that change is not
%% related to random values (\eg{}, hashcode), we discard that
%% specific slice. However, not every test case produces a stack trace
%% (\ie{}, passing tests), and thus, we guarantee that the test has
%% executing code by not instrumenting test classes and test methods.

%% \vspace{1ex}\noindent\textbf{Single compilation.}  Recompilation is a
%% major cost associated with critical
%% slicing~\cite{DBLP:conf/scam/BinkleyGHIKY15}. For example, \Fix{...\%
%%   of time in a slicing job from ORBS is due to compilation}. For that reason, our slicer uses a
%% program schemata where every statement in function bodies is guarded
%% by a branch predicate to control its activation. The slicer
%% re-executes the program with different guard configurations, recording
%% the smallest slice found. It uses a local search to find the smallest
%% slice for a given time budget. A slice is encoded as a list of flags,
%% each indicating whether or not a given guard is active. The initial
%% configuration of a slicing job has the flags set for all statements
%% covered by a given test.

%% \vspace{1ex}\noindent\textbf{Structure Awareness.}
%% ORBS is language-agnostic; it removes text from files but it does not
%% parse code. Each removal can lead to malformed
%% code. \Mar{$\leftarrow$how do we deal with this in the bytecode
%%   instrumentation?  explain...} We collect constraints of the form
%% $b\rightarrow{}a$ during code instrumentation to indicate that guard
%% $b$ is used in the region guarded by $a$, reflecting the nested
%% structure of the code. The slicer uses these constraints to prune the
%% search space of guard configurations, encoding the slice. For example,
%% it does not make sense to include statement $b$ in the slice and not
%% including statement $a$.

%% \vspace{1ex}\noindent\textbf{Clean state execution.} Re-execution of a
%% given test is necessary in Critical Slicing. However, test
%% re-execution may introduce flakiness due to side-effects in data
%% reachable from static fields. One alternative to address this problem
%% is to run each test in a separate JVM. Unfortunately, that alternative
%% is prohibitively slow. For that, we ran the slicing job in a single
%% JVM, using a test runner that is able to clean the static area of the
%% JVM as follows. At every re-execution of the critical slicer, the test
%% runner creates a new instance of a custom class loader, child of the
%% original JVM class loader.  Before loading a class, the custom class
%% loader checks in a cache whether or not the bytecodes were already
%% loaded. If not, the class file is loaded from disk and the bytecodes
%% are stored in the cache for future access. If the bytecodes were
%% previously loaded, the slicer avoids disk access by reading the data
%% directly from the cache.  To sum, the use of a new class loader
%% enables the slicer to ``reset'' the state prior to a new execution of
%% the same test~---~the objects accessible from the static area become
%% unreachable when the class loader is disposed at the end of an
%% execution.

@@

Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
which the component $j$ has been active during execution ($p = 1$) or
not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
0$).  For instance, $n_{11}(j)$ counts the number of times component
$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
whereas $n_{10}(j)$ counts the number of times component $j$ has been
involved in passing executions. We then calculate similarity to the
error vector by means of applying \emph{fault predictors} to each
component to produce a score quantifying how likely it is to be
faulty.  Components are then ranked according to such likelihood
scores and reported to the user. Ochiai is one of those fault
predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}.
The Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
\[\frac{\N{11}}{\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}}\]

\section{Critical Slicing + \sfl{}}
\label{sec:combination}

The combinination of critical slicing and \sfl{} consists of the
following steps: (1) Compute the execution spectra as discussed in
Section~\ref{sec:sfl}, (2) Compute slices associated with failing
tests, (3) Adjust the spectra computed in Step 1 with results obtained
in Step 2, and (4) Compute suspiciousness
scores. Figure~\ref{fig:illustration} illustrates the update of the
spectra and suspiciousness rankings as result of slicing the program
against the failing test $t_2$. The faulty statement in this example
is the component $c_2$.  The slice obtained from $t_2$ is $\{c_2,
c_5\}$.  Intuitively, slicing enables identification of cells in the
matrix (/spectra) whose values can be set to zero.

%% \begin{enumerate}
%% \item\label{step-spectra} Compute the execution spectra.
%% \item\label{step-slice} Compute slices associated with tests.
%% \item Adjust the spectra computed in Step~\ref{step-spectra} with
%%   results obtained in Step~\ref{step-slice}.
%% \item Compute suspiciousness scores.
%% %\item {[optional]} Filter statements covered by selected failing tests.
%% \end{enumerate}

@@

\Sof{@todo: Add a short 3-4 lines at most example based on one of our subjects} Section~\ref{sec:impl} explains the heuristics
we used to infer oracles for critical slicing that mitigates this
issue and Section~\ref{sec:eval} shows how often critical slicing
misses faulty statements.

@@

\subsection{Implementation}
\label{sec:impl}

\Mar{Sofia, I think this was way too low-level for intro and decided
  to move here. please check how to fit.}
\Fix{
A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}. \morpho{} retrieves as an output the input for \lithium{}. \lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization. \morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}. }

Two different tools were developed to support this research: \morpho{} and \lithium{}. \morpho{} was designed to calculate the suspiciousness of all statements of a project before, and after the top-k minimization performed by \lithium{} whereas \lithium{} is responsible for reducing the search domain of each \texttt{Java} class of the project for the after-\sfl{} analysis. \morpho{} uses the spectrum matrix (Figure \ref{fig:spectrum-example}), and the pair \emph{name\#location} for each statement to calculate the respective ranking. All rankings are ordered from highest to lowest ranked. This information is retrieved along with each test case stack trace in a \texttt{.json} file which serves as an output to \lithium{}. \lithium{} starts by generating the inputs (Algorithm \ref{alg:ls}, line $2$) for the top-k classes of each failing test based, mainly, on the output of \emph{morpho} ~---~ ranked list of statements and the test cases stacktraces. Then, the tool iterates each class from the top-k classes ($c$) of each test $t$. In each iteration, classes are refined using an external java program (Algorithm \ref{alg:ls}, line 6) that substitutes all the line comments ($\backslash\backslash$), block comments ($\backslash*$ to $*\backslash$) and javadoc comments ($/**$ to $*/$) using the \texttt{JavaParser}\footnote{JavaParser is available at http://javaparser.org/ (accessed November 2018).} library. This step was added to \lithium{} because it turns \texttt{MozillaLithium} faster since the empty lines are ignored. Then, \texttt{MozillaLithium} performs the class minimization using a function of interest (Algorithm \ref{alg:finc}) which compares the output of the test with the expected one which is given as an input. Finally, the location of all relevant statements (Algorithm \ref{alg:ls}, line 9) is saved in a \texttt{.json} which is used for the before-\sfl{} analysis. \morpho{} uses the output from \lithium{} to create a copy of the older spectrum matrix and updates it according to the explanation provided on Figure \ref{fig:ds-reduction} where the statements that are not in the slice of the test suffer a suspiciouness reduction. In the end, \morpho{} performs the \sfl{} analysis for both matrixes and calculates the probability of the first line being faulty, the probability of the last line being faulty, and the mean and median of the position of the faulty line in the ranking. These are the metrics used to evaluate how considerable is the improvement obtained when combining \ds{} with \sfl{}.

\begin{algorithm}[h]
	\caption{Class Minimization Algorithm}
	\label{alg:ls}
	\begin{flushleft}
		\textbf{Input:} $proj$ - project name \\
		\hspace{2.75em} $bug$ - bug number\\
		\hspace{2.75em} $k$ - number of top ranked classes\\
		\hspace{2.75em} $stk$ - expected stacktrace\\
	 \textbf{Output:} Top-k classes minimization for each test \\
	\end{flushleft}
	\begin{algorithmic}[1]
		\Procedure{lithium-slicer}{$proj$, $bug$, $k$, $stk$}
			\State $testsInfo \leftarrow$ generateInputs($proj$, $bug$, $k$, $stk$)
			\ForAll {$t \in testsInfo$}
				\State $classes \leftarrow$ getClasses($proj$, $bug$)
				\ForAll {$c \in classes$}
					\State $unc \leftarrow$ removeComments($c$)
					\State $min \leftarrow$ MozillaLithium($iFunc$, $unc$, $t$, $stk$)
				\EndFor
				\State $slicer \leftarrow$ getLocation($c$, $t$, $min$)
			\EndFor
			\State \Return $slicer$
		\EndProcedure
	\end{algorithmic}

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.0\textwidth]{figures/lithium.pdf}
	\caption{Simple illustration of the process to obtain the top-5 minimized classes from a project carrying a bug}
\end{figure*}

\subsection{Function of Interest }
\label{sec:funcofint}

@@

The \texttt{MozillaLithium} tool takes as input a function of interest that can be designed according to the problem to be solved. The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from \texttt{Java} stack traces which show the stack of functions called until the thrown of an exception. The authors assume that it is only necessary to compare both stack traces until the call where the test fails. For each chunk selected by \texttt{MozillaLithium}, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails. These operations are performed by line 3 and 4 from Algorithm 2. The result is an oracle such as the one provided in the box below:

\vspace{3mm}
\begin{myframe} \label{box:1}
java.lang.IndexOutOfBoundsException: Index: -1, Size: 1,
java.util.ArrayList.rangeCheckForAdd(ArrayList.java:643),
java.util.ArrayList.add(ArrayList.java:455),
org.jfree.data.xy.XYSeries.addOrUpdate(XYSeries.java:564),
org.jfree.data.xy.XYSeries.addOrUpdate(XYSeries.java:527),
\textbf{org.jfree.data.xy.junit.XYSeriesTests.}\\
\textbf{testBug1955483(XYSeriesTests.java:479)},\\
...
\end{myframe}

The oracle includes an exception error message (\emph{java.lang.\\IndexOutOfBoundsException: Index: -1, Size: 1}) and the program execution path until the class test where it fails (\emph{XYSeriesTests.java:479}). The regular expression \verb/Test(.*).java/ retrieves the test class position in the stack trace. If the test class is not found, the entire stack trace is compared. There is, however, an exception. When the failure is a \emph{StackOverflowError}, there is no test class mentioned in the stack trace because the exception is a runtime error. This exception is triggered when the JVM encounters a situation where there is no space for a new stack frame to be created which is, normally, the outcome of infinite recursion. Consequently, the stack trace contains many times the failed call. So, when the failure message contains a \emph{StackOverflowError}, the oracle is only considered until the call is repeated for the fifth time.

\vspace{3mm}
\begin{myframe}
	java.lang.StackOverflowError,
	sun.reflect.generics.reflectiveObjects.\linebreak
			TypeVariableImpl.hashCode(TypeVariableImpl.java:198),
	java.util.HashMap.hash(HashMap.java:362),
	java.util.HashMap.getEntry(HashMap.java:462),
	java.util.HashMap.get(HashMap.java:417),  org.mockito.internal.util.reflection.GenericMetadataSupport.
		getActualTypeArgumentFor(GenericMetadataSupport.java:182), \linebreak
	org.mockito.internal.util.reflection.GenericMetadataSupport.
	getActualTypeArgumentFor(GenericMetadataSupport.java:185),
	org.mockito.internal.util.reflection.GenericMetadataSupport.
	getActualTypeArgumentFor(GenericMetadataSupport.java:185),
	...
\end{myframe}

Some of the error messages can be different even if the test is executed with the same inputs and in the same environment. One example is the one provided in the box below, where the memory positions (\emph{class@<memory-position>}) may differ from the ones in the expected message. In order to solve this, it was designed a mechanism to check this kind of exception patterns. However, the current version of the interesting function only considers this pattern. Other patterns will be added soon into the next version of \lithium{}.

\vspace{3mm}
\begin{myframe}
	junit.framework.AssertionFailedError: \\
	expected:<org.jfree.chart.util.ShapeList@\textbf{d0e55451}> but \\ was:<org.jfree.chart.util.ShapeList@\textbf{d951b68f}>
	...
\end{myframe}

@@

\Mar{-------------------- estou aqui}

To evaluate the performance of the \comb{} combination
suggested to improve \sfl{}

This section reports results of our study to assess the impact of the
\comb{} combination.

@@

Following other recent studies, we used the \dfj{} benchmark in our
experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six subjects and \numFaults{} faults.
\lang{} is a library
that provides a set of helper utilities for the {\small\texttt{java.lang}}
API. \cmath{} is a lightweight library of self-contained
mathematics and statistics components. The \closure{} is a toolset for
turning JavaScript files into smaller scripts for faster
download and execution in the browser. \chart{} is a library with a
full-featured charts user interface for Java. \jtime{} is a
lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is
a mocking testing framework.\comments{ that enables the developer to simulate
the behavior of classes that cannot be used in unit testing.}

>>>>

@@

@@

\begin{abstract}
\Sof{@TODO}Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
\end{abstract}

@@

Software debugging is difficult. The task of locating the faulty code
(\ie{}, fault localization) is particularly challenging. For that
reason, countless automated techniques have been proposed in the past
to reduce the cost of fault localization.

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic Slicing ~\citeauthor{Agrawal:1990:DPS:93542.93576} looks for the statements
in code that influence the evaluation of the fault-revealing
assertion. Although the technique has been intensively investigated in
research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
exception.  \sfl{}~\cite{7390282}, in contrast, does not try to
recover the influence region of faulty statements. It is a black-box~
statistical fault localization method that computes suspiciousness
values associated with program entities (e.g., basic blocks). For
that, it uses coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in decreasing
order of suspiciousness. Similarly to \ds{}, \sfl{} received
tremendous attention over the years, but its applicability to support
debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been
shown useful in supporting downstream analyses, such as Automated
Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for fixes to buggy
statements. Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes.

@@

The contributions of this work are as follows:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
	\item Empirical evidence that the \comb{} combination improves 
\end{itemize}

@@

@@

We used the Mozilla Lithium tool~\footnote{Lithium is available at \url{https://github.com/MozillaSecurity/lithium} (accessed November 2018).} as the implementation
for Critical Slicing. Lithium is conceptually similar to the DD-min
Delta Debugging algorithm~\cite{zeller-hildebrandt-tse2002}, but
operates on code instead of test inputs. It takes as input a file and
produces as output a simplified version of that file that satisfies a
user-defined oracle. For dynamic slicing, the oracle is defined such
that the test produces the same failure manifestation. The Lithium
minimization process starts by determining the initial size of
chunks---in number of lines---to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search
looking for chunks to remove from the file that satisfy the
oracle. When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more line can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs can be found elsewhere\footnote{Algorithm complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (accessed November 2018).}.

@@

Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
which the component $j$ has been active during execution ($p = 1$) or
not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
0$).  For instance, $n_{11}(j)$ counts the number of times component
$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
whereas $n_{10}(j)$ counts the number of times component $j$ has been
involved in passing executions. We then calculate similarity to the
error vector by means of applying \emph{fault predictors} to each
component to produce a score quantifying how likely it is to be
faulty.  Components are then ranked according to such likelihood
scores and reported to the user. Ochiai is one of those fault
predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}.
The Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
\[ochiai = \frac{\N{11}}{\sqrt{(\N{11}+\N{01}) * (\N{11}+\N{10})}}\]

\section{\sfl{} + Critical Slicing}
\label{sec:combination}

\Sof{Maybe discuss the limitations of \sfl{} based on the capabilibility of \ds{}}The combinination of critical slicing and \sfl{} consists of the
following steps: (1) Compute the execution spectra as discussed in
Section~\ref{sec:sfl}, (2) Compute slices associated with failing
tests, (3) Adjust the spectra computed in Step 1 with results obtained
in Step 2, and (4) Compute suspiciousness
scores. Figure~\ref{fig:illustration} illustrates the update of the
spectra and suspiciousness rankings as result of slicing the program
against the failing test $t_2$. The faulty statement in this example
is the component $c_2$.  The slice obtained from $t_2$ is $\{c_2,
c_5\}$.  Intuitively, slicing enables identification of cells in the
spectra whose values can be set to zero.

@@

\vspace{3mm}
\begin{myframe} \label{box:1}
\textbf{java.lang.NullPointerException}, \\
at org.jfree.data.general.junit.DatasetUtilitiesTests.\\
testBug2849731$\_$3(DatasetUtilitiesTests.java:1299), \\
...
\end{myframe}

@@

Section~\ref{sec:oracleheuristics} explains the heuristics
we used to infer oracles for critical slicing that mitigates this
issue.

\subsection{Oracle Heuristics}
\label{sec:oracleheuristics}

% \subsection{Implementation}
% \label{sec:impl}

% \Mar{Sofia, I think this was way too low-level for intro and decided
%   to move here. please check how to fit.}
% \Fix{
% A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}. \morpho{} retrieves as an output the input for \lithium{}. \lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization. \morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}. }

% Two different tools were developed to support this research: \morpho{} and \lithium{}. \morpho{} was designed to calculate the suspiciousness of all statements of a project before, and after the top-k minimization performed by \lithium{} whereas \lithium{} is responsible for reducing the search domain of each \texttt{Java} class of the project for the after-\sfl{} analysis. \morpho{} uses the spectrum matrix (Figure \ref{fig:spectrum-example}), and the pair \emph{name\#location} for each statement to calculate the respective ranking. All rankings are ordered from highest to lowest ranked. This information is retrieved along with each test case stack trace in a \texttt{.json} file which serves as an output to \lithium{}. \lithium{} starts by generating the inputs (Algorithm \ref{alg:ls}, line $2$) for the top-k classes of each failing test based, mainly, on the output of \emph{morpho} ~---~ ranked list of statements and the test cases stacktraces. Then, the tool iterates each class from the top-k classes ($c$) of each test $t$. In each iteration, classes are refined using an external java program (Algorithm \ref{alg:ls}, line 6) that substitutes all the line comments ($\backslash\backslash$), block comments ($\backslash*$ to $*\backslash$) and javadoc comments ($/**$ to $*/$) using the \texttt{JavaParser}\footnote{JavaParser is available at http://javaparser.org/ (accessed November 2018).} library. This step was added to \lithium{} because it turns \texttt{MozillaLithium} faster since the empty lines are ignored. Then, \texttt{MozillaLithium} performs the class minimization using a function of interest (Algorithm \ref{alg:finc}) which compares the output of the test with the expected one which is given as an input. Finally, the location of all relevant statements (Algorithm \ref{alg:ls}, line 9) is saved in a \texttt{.json} which is used for the before-\sfl{} analysis. \morpho{} uses the output from \lithium{} to create a copy of the older spectrum matrix and updates it according to the explanation provided on Figure \ref{fig:ds-reduction} where the statements that are not in the slice of the test suffer a suspiciouness reduction. In the end, \morpho{} performs the \sfl{} analysis for both matrixes and calculates the probability of the first line being faulty, the probability of the last line being faulty, and the mean and median of the position of the faulty line in the ranking. These are the metrics used to evaluate how considerable is the improvement obtained when combining \ds{} with \sfl{}.

% \begin{algorithm}[h]
% 	\caption{Class Minimization Algorithm}
% 	\label{alg:ls}
% 	\begin{flushleft}
% 		\textbf{Input:} $proj$ - project name \\
% 		\hspace{2.75em} $bug$ - bug number\\
% 		\hspace{2.75em} $k$ - number of top ranked classes\\
% 		\hspace{2.75em} $stk$ - expected stacktrace\\
% 	 \textbf{Output:} Top-k classes minimization for each test \\
% 	\end{flushleft}
% 	\begin{algorithmic}[1]
% 		\Procedure{lithium-slicer}{$proj$, $bug$, $k$, $stk$}
% 			\State $testsInfo \leftarrow$ generateInputs($proj$, $bug$, $k$, $stk$)
% 			\ForAll {$t \in testsInfo$}
% 				\State $classes \leftarrow$ getClasses($proj$, $bug$)
% 				\ForAll {$c \in classes$}
% 					\State $unc \leftarrow$ removeComments($c$)
% 					\State $min \leftarrow$ MozillaLithium($iFunc$, $unc$, $t$, $stk$)
% 				\EndFor
% 				\State $slicer \leftarrow$ getLocation($c$, $t$, $min$)
% 			\EndFor
% 			\State \Return $slicer$
% 		\EndProcedure
% 	\end{algorithmic}
%
% \end{algorithm}
%
% \begin{figure*}[t]
% 	\centering
% 	\includegraphics[width=1.0\textwidth]{figures/lithium.pdf}
% 	\caption{Simple illustration of the process to obtain the top-5 minimized classes from a project carrying a bug}
% \end{figure*}
%
% \subsection{Function of Interest }
% \label{sec:funcofint}
%
%

\Sof{@TODO: Melhorar terminologia e algoritmo} Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved. The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The authors assume that it is only necessary to compare both stack traces until the call where the test fails. For each chunk under evaluation, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

@@

@@

To evaluate the impact of the \comb{} combination, the authors rcompare the cost of diagnosing faulty software programs using SFL against using \comb{} for top-5 and top-10 of classes.

@@

Following other recent studies, we used the \dfj{} benchmark in our
experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library
that provides a set of helper utilities for the {\small\texttt{java.lang}}
API. \cmath{} is a lightweight library of self-contained
mathematics and statistics components. The \closure{} is a toolset for
turning JavaScript files into smaller scripts for faster
download and execution in the browser. \chart{} is a library with a
full-featured charts user interface for Java. \jtime{} is a
lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is
a mocking testing framework.\comments{ that enables the developer to simulate
the behavior of classes that cannot be used in unit testing.}

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lccc}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}
\label{tab:df4j}
\end{table}
\normalsize
